ODGI: understanding pangenome graphs

### 2022-02-17 manuscript/fig_extract_viz_draw_position_untangle.tex
node depth, degree; MHC drawing timings

@@

        \textbf{(e)} \textit{odgi viz} color by path depth: using the Spectra color palette with 4 levels of path depths, white indicates no depth, while grey, red, and yellow indicate depth 1, 2, and greater than or equal to 3, respectively.
        Coloring by path depth, we can see that the two references present two different allele copies of the C4 genes, both of them including the HERV sequence.

>>>>

            \caption{\label{fig:odgi_layout}}

@@

        \textbf{(e)} \textit{odgi viz} color by node depth: using the Spectra color palette with 4 levels of node depths, white indicates no depth, while grey, red, and yellow indicate depth 1, 2, and greater than or equal to 3, respectively.
        Coloring by node depth, we can see that the two references present two different allele copies of the C4 genes, both of them including the HERV sequence.
